\documentclass[a4paper,10pt]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{multicol}

% Colors
\definecolor{headingblue}{RGB}{0,102,204}

% Section formatting
\titleformat{\section}{\large\bfseries\color{headingblue}}{}{0em}{}[\titlerule]
\titleformat{\subsection}{\normalsize\bfseries}{}{0em}{}

% Reduce spacing for itemize
\setlist[itemize]{noitemsep, topsep=2pt, leftmargin=0.5cm}

% Hyperlink color
\hypersetup{
    colorlinks=true,
    urlcolor=blue
}

\begin{document}

%====================
% Header
%====================
\begin{center}
    {\LARGE \textbf{Piyush Verma}}\\[2pt]
    Infrastructure Automation Developer | DevOps Engineer\\[1pt]
    \href{mailto:piyushv080@gmail.com}{piyushv080@gmail.com} $\vert$ +91-8174812109 $\vert$ 
    \href{https://www.linkedin.com/in/piyushv080/}{LinkedIn} $\vert$ 
    \href{https://github.com/piyushv080}{GitHub}
\end{center}

%====================
% Profile
%====================
\section*{Profile}
Infrastructure Automation Developer with over 4+ years of experience in Ansible Playbook development, Github Action workflow, PowerShell, Python scripting, and ServiceNow Orchestration. Skilled in infrastructure automation and ServiceNow ITSM, with a strong background in Infrastructure and Cloud services. Proven ability to develop and automate processes for efficient and scalable solutions.

%====================
% Professional Experience (Properly aligned)
%====================

\setlength{\parindent}{0pt} % remove paragraph indentation globally

\section*{Professional Experience}

\textbf{Sanofi — Infrastructure Automation Developer (DevOps Engineer)} \hfill Jun 2025 -- Present\\
Tower 100, RMZ Spire, Levels 9-15, Plot 4 - HITEC City, Hyderabad

\vspace{2mm} % space between companies

\textbf{Cognizant — Tech Lead (Sr. Infra Developer)} \hfill Jan 2024 -- May 2025\\
SEZ F3, Manyata (MBP) - Bangalore, Karnataka

\vspace{2mm} % space between companies

\textbf{HCL Technologies — Senior Analyst (Automation Developer)} \hfill Sep 2021 -- Jan 2024\\
SEZ Tower 3, Sector 126 - Noida, Uttar Pradesh


%====================
% Core Competencies (One per line)
%====================
\section*{Core Competencies}

\textbf{Primary Skills:} Ansible, Red Hat Ansible Automation Platform, AWX Tower, ServiceNow Integration Hub, Flow Designer\\[2pt]
\textbf{Infrastructure Automation:} PowerShell, Python, REST APIs, JSON, YAML, ServiceNow Administration\\[2pt]
\textbf{Cloud \& DevOps Tools:} AWS (EC2, Lambda, S3, VPC, RDS, CloudWatch, MGN), Docker, OpenShift, GitHub Actions, Git, VS Code\\[2pt]
\textbf{Scripting \& Programming:} Python, PowerShell, JavaScript, Bash\\[2pt]
\textbf{System Administration:} Linux (RHEL 8, Ubuntu), Windows Server

%====================
% Projects (Updated for Optum JD)
%====================
\section*{Projects}

\subsection*{Cyber Security Forensic Kit Deployment \hfill Aug 2025 -- Present}
\begin{itemize}
    \item Designed and automated infrastructure workflows using Ansible and GitHub Actions across Linux and Windows, implementing CI/CD principles for reliable deployment.
    \item Applied Infrastructure as Code by creating reusable automation roles and dynamic inventories for large-scale enterprise deployments.
    \item Integrated GitHub API for secure repository management and automated provisioning with branching and merge strategies.
    \item Automated artifact management with JFrog Artifactory, ensuring validation and compliance.
    \item Developed resilient automation frameworks with error handling, retry logic, and asynchronous execution for high availability.
    \item Enhanced operational efficiency through automated data collection, secure file transfers, and detailed logging for audit and compliance.
    \item Collaborated with cross-functional teams, ensuring adherence to security standards, automation best practices, and operational excellence.
\end{itemize}

\subsection*{ATLAS AWS Cloud Transformation \hfill Jun 2025 -- Aug 2025}
\begin{itemize}
    \item Led large-scale cloud migration automation, including AWS MGN agent deployment using Ansible integrated with GitHub Actions.
    \item Engineered secure connectivity between on-prem and cloud platforms via OpenShift clusters and OIDC authentication, adhering to zero-trust principles.
    \item Automated credential management by integrating CyberArk Vault and Terraform, reducing manual intervention and improving security posture.
    \item Developed IaC solutions for AWS services: automated S3 provisioning, APM tagging, and backup orchestration.
    \item Implemented ServiceNow catalog-driven automation for Linux and Windows systems, reducing request fulfillment time.
    \item Collaborated with cloud architects and security teams to align automation with enterprise governance and best practices.
\end{itemize}

\subsection*{Clario Transformation \hfill Feb 2025 -- May 2025}
\begin{itemize}
    \item Directed full-stack automation for cardiac application deployment leveraging AWX Tower, GitLab CI/CD pipelines, and Ansible for rapid and reliable releases.
    \item Architected automated RHEL 8 server provisioning using Ansible roles and VMware vCenter modules, improving consistency and reducing manual work.
    \item Integrated Ansible AWX Tower with ServiceNow for self-service automation, improving operational efficiency.
    \item Implemented dynamic JBoss application deployment strategies with survey-driven playbooks for environment-specific configuration.
    \item Optimized release cycles and system performance through CI/CD orchestration, Infrastructure as Code, and automated workflows.
\end{itemize}

\subsection*{MDT Apollo Steady State \hfill Jul 2024 -- Jan 2025}
\begin{itemize}
    \item Automated operational workflows and configuration management using Ansible CLI and VMware Aria Automation Orchestrator, improving reliability.
    \item Developed proactive monitoring scripts in Ansible and PowerShell for job alerts and application service management.
    \item Automated storage operations including NetApp volume expansions and Linux VM lifecycle management.
    \item Enhanced system stability and compliance via Infrastructure as Code practices and automated remediation workflows.
\end{itemize}

\subsection*{Lululemon - Enterprise K8s and Vancouver \hfill Jan 2024 -- Jul 2024}
\begin{itemize}
    \item Automated end-to-end service and change request workflows using ServiceNow Integration Hub, Flow Designer, and Ansible playbooks.
    \item Integrated ServiceNow with enterprise systems (REST APIs, LDAP, SSO, Azure) and configured MID servers for secure automation.
    \item Developed DNS record management and credential reset automation for Windows and Linux servers, with Teams notifications for real-time status.
    \item Implemented incident remediation automation, ensuring port readiness and WinRM connectivity.
    \item Enhanced operational resilience and compliance by embedding security best practices and IaC principles.
\end{itemize}

\subsection*{Proximus Steady State \hfill Sep 2021 -- Jan 2024}
\begin{itemize}
    \item Automated IT operations using CA Process Automation, Ansible, CyberArk Vault, and scripting languages (PowerShell, Bash).
    \item Deployed CA ITPAM, implemented SSL certificates, and developed automation scripts leveraging REST and SOAP APIs.
    \item Integrated workflows with Ansible, CyberArk Vault, iAutomate, and ServiceNow ITSM for streamlined service delivery.
    \item Automated Splunk and DXIM agent installations and documented processes on Confluence.
    \item Conducted monthly training sessions for junior team members to support knowledge sharing.
\end{itemize}

%====================
% Education & Certifications
%====================
\section*{Education \& Certifications}
\begin{itemize}
    \item \textbf{B.Tech in Computer Science}, Kanpur Institute of Technology, AKTU Lucknow — CGPA: 7.74 (2017--2021)
    \item \textbf{Certifications:} ServiceNow (CSA, CAD, Integration Hub \& Flow Designer), AWS Certified Cloud Practitioner, Ansible Automation Ascend Certified
\end{itemize}

\end{document}
